fig4

### 2020-02-11 analysis/figure-4.Rmd
now with focused and zoomed out view of fig 4

plottopgenes <- function(whichgenes, whichtissue, whichsex, mysubtitle){
  candidates  <- allvsd %>%
    filter(gene %in% whichgenes) %>%
    dplyr::mutate(sextissue = sapply(strsplit(file_name, '_vsd.csv'), "[", 1)) %>%
    dplyr::mutate(sextissue = sapply(strsplit(sextissue, '../results/DEseq2/'), "[", 2)) %>%
    dplyr::mutate(sex = sapply(strsplit(sextissue, '\\_'), "[", 1),
                tissue = sapply(strsplit(sextissue, '\\_'), "[", 2),
                treatment = sapply(strsplit(samples, '\\_'), "[", 4)) %>%
    dplyr::mutate(treatment = sapply(strsplit(treatment, '.NYNO'), "[", 1)) %>%
    dplyr::select(sex, tissue, treatment, gene, samples, counts) %>%
    filter(tissue == whichtissue)

@@

  p <- ggplot(candidates,  aes(x = treatment, y = counts, fill = treatment, color = sex)) +
    geom_boxplot() + facet_wrap(~gene, scales = "free_y") + 
    theme_B3() +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
          legend.position = "none",
          axis.title.x = element_blank(),
          strip.text = element_text(face = "italic")) +
    labs(y = mysubtitle) 
  return(p)

@@

a <- plottopgenes(hypgenes, "hypothalamus", "female", "hypothalamus") + theme(axis.text.x = element_blank())
b <- plottopgenes(pitgenes, "pituitary", "female", "pituitary") + theme(axis.text.x = element_blank())
c <- plottopgenes(gongenes, "gonad", "female", "gonads")

plot_grid(a,b,c, ncol = 1)

```

>>>>

plottopgenes <- function(whichgenes, whichtissue, whichsex, mysubtitle, whichtstages){
  candidates  <- allvsd %>%
    filter(gene %in% whichgenes) %>%
    dplyr::mutate(sextissue = sapply(strsplit(file_name, '_vsd.csv'), "[", 1)) %>%
    dplyr::mutate(sextissue = sapply(strsplit(sextissue, '../results/DEseq2/'), "[", 2)) %>%
    dplyr::mutate(sex = sapply(strsplit(sextissue, '\\_'), "[", 1),
                tissue = sapply(strsplit(sextissue, '\\_'), "[", 2),
                treatment = sapply(strsplit(samples, '\\_'), "[", 4)) %>%
    dplyr::mutate(treatment = sapply(strsplit(treatment, '.NYNO'), "[", 1)) %>%
    dplyr::select(sex, tissue, treatment, gene, samples, counts) %>%
    filter(tissue == whichtissue, sex %in% whichsex)

@@

  p <- candidates %>%
    filter(treatment %in% whichtstages) %>%
    ggplot(aes(x = treatment, y = counts, fill = treatment, color = sex)) +
    geom_boxplot() + facet_wrap(~gene, scales = "free_y") + 
    theme_B3() +
    scale_fill_manual(values = allcolors) +
    scale_color_manual(values = allcolors) +
    theme(axis.text.x = element_blank(),
          legend.position = "none",
          axis.title.x = element_blank(),
          strip.text = element_text(face = "italic")) +
    labs(y = mysubtitle) 
  return(p)

@@

a <- plottopgenes(hypgenes, "hypothalamus", c("female"), "hypothalamus", c("hatch", "n5")) 
b <- plottopgenes(pitgenes, "pituitary", c("female"), "pituitary", c("inc.d9", "inc.d17")) 
c <- plottopgenes(gongenes, "gonad", c("female"), "gonads", c("lay", "inc.d3"))

fig4a <- plot_grid(a,b,c, ncol = 1)

d <- plottopgenes(hypgenes, "hypothalamus", c("female", "male"), NULL, charlevels) 
e <- plottopgenes(pitgenes, "pituitary", c("female", "male"), NULL, charlevels) 
f <- plottopgenes(gongenes, "gonad", c("female", "male"), NULL, charlevels) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

fig4b <- plot_grid(d,e,f, ncol = 1)

fig4 <- plot_grid(fig4a, fig4b, rel_widths = c(1,2))
fig4
```
